Depression and suicidality as credible signals of need

### 2021-05-07 Paper.rmd
Commented out some lines

<!-- ## Connection to Adversity -->

@@

Our results suggest that the costs of depression and suicidality, which in mainstream theories are taken as evidence of brain dysfunction, might instead function to help victims elicit support from reluctant social partners with whom they are in conflict.

>>>>

@@

<!-- Our results suggest that the costs of depression and suicidality, which in mainstream theories are taken as evidence of brain dysfunction, might instead function to help victims elicit support from reluctant social partners with whom they are in conflict. -->
